---
name: Matthew
surname: Denman
position: "Nuclear Power Reliability Engineer"
address: "Kairos Power"
phone: +1 617 999-2848
email: "denman@kairospower.com"
github: mrdenman-nuclear
linkedin: matthew-denman-86ab3615
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```


# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy in Nuclear Engineering", "2007-2011", "Massachusetts Institute of Technology", "Cambridge MA",
  "Bachelor of Science in Nuclear Engineering", "2003-2007", "University of Florida", "Gainesville, FL"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Work History


```{r}
tribble(
  ~ Employeer, ~ Year, ~ Position, ~ Where,
  "Kairos Power", "2019-Present", "Principal Engineer, Reliability Engineering", "Albuquerque, NM"
) %>% 
  detailed_entries(Employeer, Year, Position, Where)
```

* Responsible Engineer, architect, and lead modeler for the Hermes reactor's
Maximum Hypothetical Accident (MHA). The Hermes MHA is the first MHA developed
specifically for a reactor with a "functional containment" safety case. 

* Responsible Engineer for the Hermes reactor's Steady State Effluent Release 
and associated off-site dose methodology development and analysis. 

* Responsible Engineer for the KP-FHR Mechanistic Source Term (MST) methodology
development project which resulted in the first Nuclear Regulatory Commission
(NRC) approved topical report for "functional containment" source terms. 


\vspace{10pt}

```{r}
tribble(
  ~ Employeer, ~ Year, ~ Position, ~ Where,
  "Sandia National Laboratories, Nuclear Energy Systems", "2017-2019", "Principal Member of the Techncial Staff", "Albuquerque, NM"
) %>% 
  detailed_entries(Employeer, Year, Position, Where)
```

* Principal Investigator for the reconstitution of the Centralized Reliability Database Organization (CREDO) database to support Probabilistic Risk Assessments and Safety Analysis for Sodium Fast Reactors (SFRs).

* Principal Investigator for an NRC Office of New Reactors funded evaluation of scoping source terms for non-light water reactors reactors.


\vspace{10pt}

```{r}
tribble(
  ~ Employeer, ~ Year, ~ Position, ~ Where,
  "Sandia National Laboratories, Nuclear Energy Systems", "2011-2017", "Senior Member of the Techncial Staff", "Albuquerque, NM"
) %>% 
  detailed_entries(Employeer, Year, Position, Where)
```


* Principal Investigator for:
    * a multi-institute, multi-disciplinary examination of safety and licensing gaps for the Sodium Fast Reactor.
    * a LDRD project to create the mathematical formulation for Dynamic Fault Trees to inform decision makers of evolving state of support system success probability mid-accident.
    * a two proof-of-concept Level 2 Risk Assessments to inform the development of Severe Accident Management Guidelines for both integral Pressurized Water Reactors and SFRs.


* Investigator responsible for:
    * the development of uncertainty distributions for Safety Relief Valve failure, Safety Vent Valve failure, Decay Heat, and Core Collapse parameters in the Surry and Sequoyah SOARCA Uncertainty Analysis.
    * characterizing of uncertainties and sensitivity studies on the Fukushima 1F1 accident analysis using MELCOR.



# Professional Society Postions


```{r}
tribble(
  ~ Group, ~ Year, ~ Position, ~ Responsibility,
  "Sub-Committee of Standards Integration", "2022-Present", "Chair", "Facilitating New Standards",
    "Advanced Reactor Safety (ARS) Program Committee", "2021-Present", "Chair", "Organize the revival of the ARS conference series.",
) %>% 
  detailed_entries(Group, Year, Position, Responsibility)
```



 
# Publications

```{r}
vitae::bibliography_entries(here::here("Jan2023", 'ten.bib'))
```


# Patent

Dynamic, risk informed decision support systems and methods; US-10997513-B1. Issued May 4, 2021; https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/10997513
